---
output: github_document
number_sections: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Purpose of corr2D

[![CRAN version](http://www.r-pkg.org/badges/version/corr2D)](http://cran.r-project.org/package=corr2D)
![cranlogs](http://cranlogs.r-pkg.org./badges/corr2D)

The package corr2D implements two-dimensional (2D) correlation analysis in R.
It allows the user to calculate and plot homo as well as hetero 2D correlation
spectra from an input matrix containing the (preprocessed) spectra. The user
can freely choose the reference spectrum used to create the dynamic spectra,
how the perturbation variables vector should be handled, if and how the
resulting 2D spectra should be scaled and how many cores should be used to
calculate the correlation matrix.  
The plot functions offer a wide variety of options to customize the look
of 2D spectra. In this context the appearance of the main spectrum can be
altered and the 1D reference spectra as well as the color legend can be
controlled.  
The package also features an example dataset containing preprocessed FT-Raman
spectra of a self-healing polymer sample.

# How to use corr2D on a simple example

First we need to make the package available and get an example dataset. For illustration purposes we use the
FuranMale dataset from the present corr2D package.
```{r}
library("corr2D")
data(FuranMale, package = "corr2D")
```

As the next step we calculate the homo 2D correlation spectra of the FuranMale dataset
using the function corr2d() and the first spectrum of the dataset as reference
spectrum.
```{r}
twod <- corr2d(FuranMale, Ref1 = FuranMale[1, ], corenumber = 1)
```

The last step is to plot the resulting 2D correlation spectra. As an example we
plot the synchronous correlation spectrum of the FuranMale dataset. The
appearance of the 2D plot can be altered by i.e. using the xlab and ylab
options to control the labels at the x- and y-axes.
```{r}
plot_corr2d(twod, xlab = expression(paste("relative Wavenumber" / cm^-1)),
                  ylab = expression(paste("relative Wavenumber" / cm^-1)))
```    

For an in-depth tutorial as well as a detailed description of the code see R. Geitner et al. (2019) <DOI:10.18637/jss.v090.i03>.